Refunctionalization of Abstract Abstract Machines (Functional Pearl)

### 2018-06-28 paper/paper.tex
Minor grammer, whitespace

In the domain of abstract semantic artifacts, by contrast, the relations between small-step
abstract abstract machines and big-step abstract definitional interpreters, as well as the
question of deriving one from the other, are not well studied.
One of the fundamental differences between concrete semantic artifacts and abstract semantic
artifacts is that a sound instance of the latter must tell you facts about all possible execution paths, and
thus introduce nondeterminism. In addition to ensuring termination, abstract semantic
artifacts are usually equipped with a cache of reachable states; the cache is
updated in a monotonic way and guaranteed to reach the least fixed-point eventually.
In this functional pearl, we make a first step in answering the question of interderiving
abstract semantics artifacts, and provide a constructive answer to relate AAMs and ADIs
by presenting a series of syntactic transformations on the program from small-step
abstract abstract machines to big-step abstract definitional interpreters.

@@

We begin by reviewing some background necessary for this work in Section~\ref{background}, 
as well as introducing some of the basic code structures used throughout the paper. 
We then address the main contribution of this paper: bridging the gap between
small-step AAM and big-step ADI by applying a series of well-known systematic transformations
drawn from concrete semantic artifacts.
Those transformations are shown in Figure~\ref{fig:trans} and summarized here, with full
descriptions in their respective associated sections:

@@

These transformations are used throughout the paper, with refunctionalization and
defunctionalization of abstract interpreters playing important roles for the stack model of
the analyzed language. By refunctionalization, the call structure of the analyzed language
is blended into the call structure of the defining language. This provides another perspective to
explain why \citeauthor{darais2017abstracting}'s abstract definitional interpreters
is able to inherit the pushdown control-flow property from its defining language.

>>>>

In the domain of abstract semantic artifacts, by contrast, the relations between small-step
abstract abstract machines and big-step abstract definitional interpreters, as well as the
question of deriving one from the other, are not well studied.
One of the fundamental differences between concrete semantic artifacts and abstract semantic
artifacts is that a sound instance of the latter must tell you facts about all possible execution paths, and
thus introduce nondeterminism. In addition to ensuring termination, abstract semantic
artifacts are usually equipped with a cache of reachable states; the cache is
updated in a monotonic way and guaranteed to reach the least fixed-point eventually.
In this functional pearl, we make a first step in answering the question of interderiving
abstract semantics artifacts, and provide a constructive answer to relate AAM and ADI
by presenting a series of syntactic transformations on the program from small-step
abstract abstract machines to big-step abstract definitional interpreters.

@@

We begin by reviewing some background necessary for this work in Section~\ref{background},
as well as by introducing some of the basic code structures used throughout the paper.
We then address the main contribution of this paper: bridging the gap between
small-step AAM and big-step ADI by applying a series of well-known systematic transformations
drawn from concrete semantic artifacts.
Those transformations are shown in Figure~\ref{fig:trans} and summarized here, with full
descriptions in their respective associated sections:

@@

These transformations are used throughout the paper, with the refunctionalization and
defunctionalization of abstract interpreters playing important roles for the stack model of
the analyzed language. By refunctionalization, the call structure of the analyzed language
is blended into the call structure of the defining language. This provides another perspective to
explain why \citeauthor{darais2017abstracting}'s abstract definitional interpreter
is able to inherit the pushdown control-flow property from its defining language.
